---
# name: Ali
surname: Ali Guner
position: "Professor of Surgery"
address: "Karadeniz Technical University, Faculty of Medicine, Trabzon, Turkey"
# phone: +90 506 ....
profilepic: "images/ag_2019.jpg"
www: aliguner.com
email: "draliguner@yahoo.com"
twitter: AliGunerMD
github: AliGunerMD
orcid: 0000-0001-7801-8081
publons: "Q-2744-2015"
googlescholar: "-WX7tXMAAAAJ"
# linkedin: 
date: "`r format(Sys.time(), '%B %Y')`"
# aboutme: 
headcolor: 414141
output: 
  vitae::awesomecv:
    page_total: true
editor_options: 
  chunk_output_type: console
---
<!-- "awesome-cv.cls" file has been mildly modified. 
mainly for "For elements of entry" lines.-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(scholar)
library(glue)
```



```{r functions}
# an Excel file is needed. All subcategory should be included into the different sheets.

readExcelSheets <- function(filename){
  all <- readxl::excel_sheets(filename)
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  names(list) <- all
  invisible(list2env(list, envir = .GlobalEnv))
}

filename <- here::here("myCV", "data", "cv_data_2023.xlsx")
readExcelSheets(filename)

```

# Who I am

 * A surgeon who has lost his mind with the treatment of gastric cancer..  
 * An academic who enjoys to play with computers..  
 * A data scientist who believes that the future of science is in data..  
 * A visionary waiting for the irony of artificial intelligence to turn into reality..  
 * A photographer in pursuit of the abstract details of the universe..  
 * Epicurean..  
 
# Education

```{r}
education %>% 
  detailed_entries( 
          with = degree,
          what = institution,
          when = year,
          where = where,
          why = NULL)
          
```


<!-- # Language level -->

```{r, eval=FALSE}
language_exam <- tribble(
        ~exam, ~language, ~year, ~degree,
        "YDS", "English", "2016", 83.75,
        "YÖKDİL", "English", "2017", 96.25
)

language_exam %>% 
        brief_entries( 
                what = glue::glue("{exam} - {language} ({year})", .na = ""),
                with = glue::glue("{degree}/100", .na = ""),
                )
```

 
# Associations

```{r}
association %>% 
        brief_entries( 
                with = glue::glue("{year_start} - {year_end}", .na = ""),
                what = name
                )

```


# Classes

```{r}
class %>% 
        select(-isim) %>% 
        detailed_entries( 
                # what = level,
                where = glue("{institute} - {level}") ,
                with = period,
                why = name
                )

```




# Publications

```{r}
# https://scholar.google.com/citations?view_op=list_works&hl=tr&hl=tr&user=-WX7tXMAAAAJ&pagesize=100&sortby=pubdate

# https://www.webofscience.com/wos/author/record/Q-2744-2015

my_id <- "-WX7tXMAAAAJ"
my_profile <- get_profile(my_id)


imported_pubs <- scholar::format_publications(my_id, author.name =  "A Guner") %>% as_tibble() %>% 
        mutate(value = str_replace_all(value, "Güner", "Guner"),
               row_id = row_number(),
               value = glue::glue("{row_id}. {value}"))

# get_citation_history(my_id)
```

I have **`r nrow(imported_pubs)`** published articles.  
Total number of the citations for the `r nrow(imported_pubs)` articles: `r my_profile$total_cites`.  
h-index (based on the [Google Scholar](https://scholar.google.com/citations?view_op=list_works&hl=tr&hl=tr&user=-WX7tXMAAAAJ&pagesize=100&sortby=pubdate)): `r my_profile$h_index`.   
i-10 index: `r my_profile$i10_index`.  
h-index (Web of Science): 19 (manually added).    


```{r, results = "asis"}

imported_pubs$value %>% 
        cat(sep='\n\n')


# get_publications(my_id) %>%
#         as_tibble() %>% 
#          arrange(desc(year)) %>% View()



# scholar::get_publications("-WX7tXMAAAAJ") %>%
#         as_tibble() %>% 
#         arrange(desc(year)) %>% 
#         mutate(year = as.character(year),
#                row_id = row_number(),
#                journal = str_to_title(journal)) %>% 
#         detailed_entries(
#     what = title,
#     when = pubid,
#     with = glue::glue("{row_id}. {author}", .na = "") ,
#     where = journal,
#     why = glue::glue("{year}. {number}", .na = "")
#   )


```

# Invited talks

```{r}
invitation %>% 
        arrange(desc(year)) %>% 
        detailed_entries( 
                what = glue::glue("{role}: {congress}", .na = ""),
                when = glue::glue("{month}/{year}", .na = ""),
                where = city,
                # with = role,
                why = details
                )

```




# Abstracts

```{r, eval=FALSE}
abstract %>% 
        arrange(desc(year)) %>% 
        detailed_entries( 
                # what = authors,
                when = glue::glue("{year}/{city}", .na = ""),
                with = authors,
                what = glue::glue("{number} {congress}", .na = ""),
                why = title
                )

```

```{r, results = "asis"}
abstract %>% 
        arrange(desc(year)) %>% 
        mutate(row_id = row_number() ,
               value = glue("{row_id}. {authors} ({number}) {title}. {congress} - {year}/{city}.", .na = "")) %>% 
        pull(value) %>% 
        cat(sep='\n\n')

```


# Books
```{r}
book %>% 
        mutate(year = parse_number(editor)) %>% 
        arrange(desc(year)) %>% 
        detailed_entries( 
                what = glue::glue("{book} ({editor})", .na = ""),
                when = type,
                # where = glue::glue("{author} ({editor})", .na = ""),
                # with = name,
                why = glue::glue("{name} (Authors: {author})", .na = ""),
                )

```


# Courses
```{r}
course %>% 
        arrange(desc(year)) %>% 
        detailed_entries(
                what = name,
                # when = year,
                # with = authors,
                when = glue::glue("{year}/{city}", .na = ""))
```


# Congress
```{r}
congress %>% 
        separate_rows(position, sep = ",") %>% 
        arrange(desc(year)) %>% 
        detailed_entries(
                what = name,
                # when = year,
                # with = authors,
                when = glue::glue("{year}/{city}", .na = ""),
                why = position)
```


# Others
```{r}
others %>% 
        arrange(type) %>% 
        brief_entries(
                # where = type,
                # when = year,
                # with = authors,
                with = glue::glue("{date_start} - {date_end}", .na = ""),
                what = glue::glue("{definition} ({affiliation})", .na = ""))
```













```{r, eval=FALSE}

# knitr::write_bib(c("vitae", "tibble"), "ag_bibtex_2022_03.bib")

bibliography_entries("ag_bibtex_20230222.bib") 
```


```{r, eval=FALSE}

library("bib2df")
bib_df <- bib2df(here::here("myCV", "ag_bibtex_20230225.bib"))  
        
my_bib_df <- bib_df %>% 
        arrange(desc(YEAR))

df2bib(my_bib_df, file = here::here("myCV", "sorted_ag_bibtex_20230222.bib"))

```
  

===============================================================================================
  
  
**Last update:** `r format(Sys.time(), "%d %b %Y %X")`   
This CV was prepared with *[vitae](https://github.com/mitchelloharawild/vitae)* and *[scholar](https://github.com/jkeirstead/scholar)* (with the help of Microsoft Excel and Google Scholar) in RStudio.
